UQWorld: an Applied UQ Community

### 2019-05-08 latex/uqworld-presentation.tex
Update slides

Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.

>>>>

Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users\footnote{not to mention it fits this sentence: \emph{It promotes an active collaboration with research groups in ETH and in other universities in order to disseminate the good practices and associated tools for uncertainty quantification}. UQLab is not a pre-requisite.}.
%in context
\vspace{0.3cm}
